---
title: "Assignment_9"
author: "Kai Pauole"
date: "2026-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data 
Here I will inspect the data GradSchool_Admissions and predict the chances of graduating. 

```{r}
# load packages
library(tidyverse)
library(ggplot2)
library(easystats)
library(broom)

# load data
graduation = read.csv("GradSchool_Admissions.csv")
```

```{r}
head(graduation)
str(graduation)
```
Data need to be cleaned a bit. Rank needs to change to a factor. Also need to look for any missing values.

```{r}
# Convert rank to factor
graduation$rank <- as.factor(graduation$rank)

# check for na or missing
sum(is.na(graduation))

```
## Exploratory Data Analysis

First I will look at GPA vs. admit
```{r}
ggplot(graduation, aes(x = gpa, fill = factor(admit))) +
  geom_density(alpha = 0.5) +
  labs(fill = "Admit")
```
This shows that even if someone got a high GPA does not guarantee acceptance, but your chances are higher. 


Second GRV vs. admit
```{r}
ggplot(graduation, aes(x = gre, fill = factor(admit))) +
  geom_density(alpha = 0.5) +
  labs(fill = "Admit")
```
This shows that Even with a high GRE you also do not have a chance of getting in, but your chances are higher.


Lastly rank vs. admit, because of the values of rank I will just use a bar graph
```{r}
ggplot(graduation, aes(x = rank, fill = factor(admit))) + geom_bar(position = 'fill') + labs(y = 'admitted')
```
This does seem to show that rank of the institution you attend increases the chance of getting admitted. 

How do these correlate? Lets explore. 
```{r}
mod1 = glm(admit ~ gre + gpa + rank,
              data = graduation,
              family = binomial)

summary(mod1)
```
Rank, gpa, and gre together are needed to make the best predictions.

## Predictions 

Here we will make predictions 
```{r}
graduation$predicted_prob = predict(mod1, type = "response")

head(graduation)
```

This shows the probability of getting admitted based on all three values.







